Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex

\begin{table}[hbtp]
\centering
{\small
\caption{Regex vs. Comby for Python, including redundant mutants.}
\label{tab:table_pyrust}
\begin{tabularx}{\columnwidth}{X|r|rcr|rcr}
\toprule\toprule
                 &                 & \multicolumn{3}{c|}{\textbf{Regex}}             &\multicolumn{3}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & red.  & $\frac{valid}{total}$ & \textbf{\%} & red. & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
keract           & 402             & 729       & $\frac{1655}{3984}$   & 41.53\%     & 533       & $\frac{1471}{3067}$   & 47.96\% \\[1ex]
dtw              & ... \\
%
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrrrrr}
                  && &  Red.     & Valid  & Invalid  & \% \\\midrule
\multirow{4}{*}{Overall} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & \\
    &   &  Std. Dev & 584.79  & 708.93 & 813.35 & 11.06\%  \\
 & \multirow{2}{*}{Comby} & Mean & 839.33 & 840.67 & 416.67 & 35.84\% \\
  &   &  Std. Dev &  211.62 & 628.79 & 418.99 & 12.28\%   \\
\end{tabularx}}
\end{table}

>>>>

\begin{table}[hbtp]
\centering
{\small
\caption{Regex vs. Comby for Python, including redundant mutants.}
\label{tab:table_pyrust}
\begin{tabularx}{\columnwidth}{X|r|rcr|rcr}
\toprule\toprule
                 &                 & \multicolumn{3}{c|}{\textbf{Regex}}             &\multicolumn{3}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & red.  & $\frac{valid}{total}$ & \textbf{\%} & red. & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
keract           & 402             & 729       & $\frac{1655}{3984}$   & 41.53\%     & 533       & $\frac{1471}{3067}$   & 47.96\% \\[1ex]
dtw              & 118             & 567       & $\frac{973}{2106}$   & 46.20\%     & 639       & $\frac{866}{1835}$   & 47.19\% \\[1ex]
notion-sdk-py    & 189             & 82        & $\frac{196}{1038}$   & 18.89\%     & 122       & $\frac{196}{1019}$   & 19.23\% \\[1ex]
atlassian-python-api    & 236             & 207        & $\frac{302}{1541}$   & 19.99\%     & 351       & $\frac{333}{1319}$   & 25.25\% \\[1ex]
ESD              & 698            & 1642      & $\frac{1859}{6268}$   & 29.46\%     & 614       & $\frac{1712}{3874}$   & 44.18\% \\[1ex]
fiber            & 358            & 163      & $\frac{493}{1565}$   & 31.08\%     & 241       & $\frac{458}{1466}$   & 31.24\% \\[1ex]
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrrrrr}
                  && &  Red.     & Valid  & Invalid  & \% \\\midrule
\multirow{4}{*}{Overall} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & \\
    &   &  Std. Dev & 584.79  & 708.93 & 813.35 & 11.06\%  \\
 & \multirow{2}{*}{Comby} & Mean & 839.33 & 840.67 & 416.67 & 35.84\% \\
  &   &  Std. Dev &  211.62 & 628.79 & 418.99 & 12.28\%   \\
\end{tabularx}}
\end{table}
